---
title: "Assignment_4"
output:
  word_document: default
  html_document: default
  pdf_document: default
date: "2022-10-29"
---
```{r}
DF <- read.csv("~/Downloads/Pharmaceuticals.csv")
```

```{r}
library(tidyverse)
library(factoextra)
library(ISLR)
library(flexclust)
```
```{r}
df <- DF[,c(3:11)]
summary(df)
```
```{r}
df <- scale(df)
distance <- get_dist(df)
fviz_dist(distance)
```
```{r}
k4 <-kmeans(df, centers = 5, nstart = 10)
k4$center
k4$size
fviz_cluster(k4, data = df)
```
```{r}
k4 = kcca(df, k=5, kccaFamily("kmedians"))
k4
```
```{r}
clusters_index <- predict(k4)
image(k4)
points(df, col=clusters_index, pch=19, cex=0.3)
```

```{r}
fviz_nbclust(df, kmeans, method = "wss")
fviz_nbclust(df, kmeans, method = "silhouette")
```
B. Cluster 1 has lowest Leverage.

Cluster 2 has highest PE ratio, lowest ROE, lowest ROA, lowest Asset Turnover, lowest Net Profit Margin

Cluster 3 has highest Market Cap, highest ROE, highest ROA, highest Asset Turnover

Cluster 4 has highest Beta, highest Leverage, highest Rev growth and lowest Market Cap.

Cluster 5 has highest Net Profit Margin, lowest Beta, lowest PE Ratio, lowest Rev growth.

C. There is pattern in the clusters with respect to Media recommendation variable. Cluster 5 with highest Net Profit Margin, lowest Beta, lowest PE Ratio, lowest Rev growth have mostly Hold recommendation.

D. We can name various clusters based on their dependence on the quantitative variables.

Cluster 1 - Lowest Leverage cluster

Cluster 2 - High PE ratio, Low ROE, ROA, Asset Turnover, Net Profit Margin Cluster

Cluster 3 - High Market Cap, ROE, ROA, Asset Turnover cluster

Cluster 4 - High Beta, Leverage, Rev growth and Low Market Cap cluster

Cluster 5 - High Net Profit Margin, Low Beta, PE Ratio, Rev growth cluster


